Format for lefse and run on the classes CR and tox

### 2019-11-03 scripts/13_PCoA_brayCurtis_KO_abundance.Rmd
update

# ggplot 
pc_bc %>% 
  as.data.frame() %>% 
  rownames_to_column('Sampleid') %>% 
  full_join(uppheno, by = 'Sampleid') %>% 
  ggdotplot(x  = 'V1', y = 'V2', color =  'Toxicity', fill = 'Toxicity', 
            palette = 'lancet')

>>>>

# ggplot 
pc_bc %>% 
  as.data.frame() %>% 
  rownames_to_column('Sampleid') %>% 
  full_join(uppheno, by = 'Sampleid') %>% 
  ggplot(aes(x  = V1, y = V2, color =  Toxicity, fill = Toxicity)) +
  geom_point() +
  labs(x = 'PCo 1', y = 'PCo 2', title = 'PCoA plot for response to Toxicity') +
  theme_classic() +
  scale_color_manual(values = c('#42B440', '#EC0000'))  +
  scale_fill_manual(values = c('#42B440', '#EC0000')) +
  ggsave('../figs/PCoA/response_tox.jpg', dpi = 300, width = 6, height = 5)

pc_bc %>% 
  as.data.frame() %>% 
  rownames_to_column('Sampleid') %>% 
  full_join(uppheno, by = 'Sampleid') %>% 
  ggplot(aes(x  = V1, y = V2, color =  CR, fill = CR)) +
  geom_point() +
  labs(x = 'PCo 1', y = 'PCo 2', title = 'PCoA plot for response to CR') +
  theme_classic() +
  scale_color_manual(values = c('#42B440', '#EC0000'))  +
  scale_fill_manual(values = c('#42B440', '#EC0000')) +
  ggsave('../figs/PCoA/response_CR.jpg', dpi = 300, width = 6, height = 5)

pc_bc %>% 
  as.data.frame() %>% 
  rownames_to_column('Sampleid') %>% 
  full_join(uppheno, by = 'Sampleid') %>% 
  ggplot(aes(x  = V1, y = V2, color =  ORR, fill = ORR)) +
  geom_point() +
  labs(x = 'PCo 1', y = 'PCo 2', title = 'PCoA plot for response to ORR') +
  theme_classic() +
  scale_color_manual(values = c('#42B440', '#EC0000'))  +
  scale_fill_manual(values = c('#42B440', '#EC0000')) +
  ggsave('../figs/PCoA/response_ORR.jpg', dpi = 300, width = 6, height = 5) 
```

### 2019-11-03 scripts/18_lefse_metaphlan2_CR_tox.Rmd
update

```{r}
# get different combination of the classes
classes <- c('CR', 'Toxicity')
subclass <- c('Disease_Class')

@@

```{r}
# input: relative abundance unstratified for pathway abundance
relab <- read_tsv('../data/humann2_res/humann2_final_out/humann2_pathabundance_cpm_unstratified.tsv') %>% 
  rename(sampleid = names(.)[1]) %>% 
  rename_all(funs(str_replace(., '_Abundance$',''))) %>% 
  # remove the unmapped and the unintegrated record
  filter(!sampleid %in% c('UNMAPPED','UNINTEGRATED'))

# see if the sampleid in the relab is clean(do I need to clean additionally)
all.equal(sort(pheno$Sampleid), sort(colnames(relab)[2:ncol(relab)]))

# reorder the relab column to be the same with pheno table
relab_or <- bind_cols(relab[,1],relab[,pheno$Sampleid])

# just to be sure
all.equal(colnames(relab_or)[2:ncol(relab_or)], pheno$Sampleid)

# write out the table
relab_or %>% 
  write_tsv('../data/pheno_aligned_relab_table/humann2_pathabundance_cpm_unstratified.tsv')
```

@@

```{r}
# create the commad in df with str_glue and then output to a bash script
pheno_combi <- tibble(pheno_file = list.files('../data/lefse_input', pattern = '.txt$', full.names = T)) %>% 
  mutate(combi = str_extract(pheno_file, 'pheno.+\\.'))

>>>>

```{r}
# get different combination of the classes
classes <- c('CR', 'Toxicity')
subclass <- c('Disease_Status_CAR')

@@

```{r}
spp <- read_csv('../data/metaphlan2_result/merged_abundance_table_species_reordered.txt')

all.equal(colnames(spp)[2:ncol(spp)], pheno$Sampleid)
```

@@

```{r}
# create the commad in df with str_glue and then output to a bash script
pheno_combi <- tibble(pheno_file = list.files('../data/lefse_input', pattern = 'Disease_Status_CAR.txt$', full.names = T)) %>% 
  mutate(combi = str_extract(pheno_file, 'pheno.+\\.'))
